---
title: "Functional"
author: "Justin Harder"
date: "10/11/2019"
output: html_document
---


```{r setup, include=FALSE}
''''
setwd("C:/Users/Exiz/Documents/DataScience/Munging/Munging_project/MUNGE_MUNGE_MUNGE/")
scorecard <- read.csv(file = "Data/data_scorecard.csv",na.strings = c(""))
scorecard$X09.10.Net.price.public
''''
scorecard.df <- read.csv("C:/Users/Manda/Documents/Data-Munging/CollegeScorecard_Raw_Data/sep-sheets/filtered-all-years.csv", na.strings = c('') )
scorecard.df

```

```{r}
income_groups_08.09 <- c("X09.10.Net.price.public","X09.10.0.30k.net.price.public", "X09.10.30.48k.net.price.public" , "X09.10.48.75k.net.price.public" ,"X09.10.75.110k.net.price.public" , "X09.10.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for lowest income group
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumalitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumalitive <- cumalitive + abs(as.numeric(burden[,i]))
  }
  return(cumalitive)
}
poop <- variance_of_colleges(scorecard, income_groups_08.09)
sum(is.na(poop))
```
### Years 09-10

```{r}

income_groups_09.10 <- c("X09.10.Net.price.public","X09.10.0.30k.net.price.public", "X09.10.30.48k.net.price.public" , "X09.10.48.75k.net.price.public" ,"X09.10.75.110k.net.price.public" , "X09.10.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X09.10.variance <- variance_of_colleges(scorecard, income_groups_09.10)

```

## Including Plots - 09-10

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X09.10.variance))
X09.10.variance.min <- summary(X09.10.variance)[[1]]
X09.10.variance.max <- summary(X09.10.variance )[[6]]

X09.10.accessibility.metric <- resizing(global_max = X09.10.variance.max , global_min = X09.10.variance.min, X09.10.variance)
summary(X09.10.accessibility.metric) 


```

### Years 10-11

```{r}

income_groups_10.11 <- c("X10.11.Net.price.public","X10.11.0.30k.net.price.public", "X10.11.30.48k.net.price.public" , "X10.11.48.75k.net.price.public" ,"X10.11.75.110k.net.price.public" , "X10.11.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X10.11.variance <- variance_of_colleges(scorecard, income_groups_10.11)

```

## Including Plots 10-11

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X10.11.variance))
X10.11.variance.min <- summary(X10.11.variance)[[1]]
X10.11.variance.max <- summary(X10.11.variance )[[6]]

X10.11.accessibility.metric <- resizing(global_max = X10.11.variance.max , global_min = X10.11.variance.min, X10.11.variance)
summary(X10.11.accessibility.metric) 


```

### Years 11-12

```{r}

income_groups_11.12 <- c("X11.12.Net.price.public","X11.12.0.30k.net.price.public", "X11.12.30.48k.net.price.public" , "X11.12.48.75k.net.price.public" ,"X11.12.75.110k.net.price.public" , "X11.12.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X11.12.variance <- variance_of_colleges(scorecard, income_groups_11.12)

```

## Including Plots 11-12

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X11.12.variance))
X11.12.variance.min <- summary(X11.12.variance)[[1]]
X11.12.variance.max <- summary(X11.12.variance )[[6]]

X11.12.accessibility.metric <- resizing(global_max = X11.12.variance.max , global_min = X11.12.variance.min, X11.12.variance)
summary(X11.12.accessibility.metric) 


```

### Years 12-13

```{r}

income_groups_12.13 <- c("X12.13.Net.price.public","X12.13.0.30k.net.price.public", "X12.13.30.48k.net.price.public" , "X12.13.48.75k.net.price.public" ,"X12.13.75.110k.net.price.public" , "X12.13.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X12.13.variance <- variance_of_colleges(scorecard, income_groups_12.13)

```

## Including Plots 12-13

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X12.13.variance))
X12.13.variance.min <- summary(X12.13.variance)[[1]]
X12.13.variance.max <- summary(X12.13.variance )[[6]]

X12.13.accessibility.metric <- resizing(global_max = X12.13.variance.max , global_min = X12.13.variance.min, X12.13.variance)
summary(X12.13.accessibility.metric) 


```

### Years 13-14

```{r}

income_groups_13.14 <- c("X13.14.Net.price.public","X13.14.0.30k.net.price.public", "X13.14.30.48k.net.price.public" , "X13.14.48.75k.net.price.public" ,"X13.14.75.110k.net.price.public" , "X13.14.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X13.14.variance <- variance_of_colleges(scorecard, income_groups_13.14)

```

## Including Plots 13-14

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X13.14.variance))
X13.14.variance.min <- summary(X13.14.variance)[[1]]
X13.14.variance.max <- summary(X13.14.variance )[[6]]

X13.14.accessibility.metric <- resizing(global_max = X13.14.variance.max , global_min = X13.14.variance.min, X13.14.variance)
summary(X13.14.accessibility.metric) 


```

### Years 14-15

```{r}

income_groups_14.15 <- c("X14.15.Net.price.public","X14.15.0.30k.net.price.public", "X14.15.30.48k.net.price.public" , "X14.15.48.75k.net.price.public" ,"X14.15.75.110k.net.price.public" , "X14.15.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X14.15.variance <- variance_of_colleges(scorecard, income_groups_14.15)

```

## Including Plots 14-15

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X14.15.variance))
X14.15.variance.min <- summary(X14.15.variance)[[1]]
X14.15.variance.max <- summary(X14.15.variance )[[6]]

X14.15.accessibility.metric <- resizing(global_max = X14.15.variance.max , global_min = X14.15.variance.min, X14.15.variance)
summary(X14.15.accessibility.metric) 


```

### Years 15-16

```{r}

income_groups_15.16 <- c("X15.16.Net.price.public","X15.16.0.30k.net.price.public", "X15.16.30.48k.net.price.public" , "X15.16.48.75k.net.price.public" ,"X15.16.75.110k.net.price.public" , "X15.16.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X15.16.variance <- variance_of_colleges(scorecard, income_groups_15.16)

```

## Including Plots 15-16

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X15.16.variance))
X15.16.variance.min <- summary(X15.16.variance)[[1]]
X15.16.variance.max <- summary(X15.16.variance )[[6]]

X15.16.accessibility.metric <- resizing(global_max = X15.16.variance.max , global_min = X15.16.variance.min, X15.16.variance)
summary(X15.16.accessibility.metric) 


```

### Years 16-17

```{r}

income_groups_16.17 <- c("X16.17.Net.price.public","X16.17.0.30k.net.price.public", "X16.17.30.48k.net.price.public" , "X16.17.48.75k.net.price.public" ,"X16.17.75.110k.net.price.public" , "X16.17.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X16.17.variance <- variance_of_colleges(scorecard, income_groups_16.17)

```

## Including Plots 16-17

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X16.17.variance))
X16.17.variance.min <- summary(X16.17.variance)[[1]]
X16.17.variance.max <- summary(X16.17.variance )[[6]]

X16.17.accessibility.metric <- resizing(global_max = X16.17.variance.max , global_min = X16.17.variance.min, X16.17.variance)
summary(X16.17.accessibility.metric) 


```


### Years 17-18

```{r}

income_groups_17.18 <- c("X17.18.Net.price.public","X17.18.0.30k.net.price.public", "X17.18.30.48k.net.price.public" , "X17.18.48.75k.net.price.public" ,"X17.18.75.110k.net.price.public" , "X17.18.110k.net.price.public")


variance_of_colleges <- function(dataframe, column_names_vector){
  #We can change this to simply work on vectors, or whatever we need for functionality
  # Only like this for "backbone".
  atc  <- as.numeric(c(unlist(dataframe[column_names_vector[1]]))) #average tuition cost
  ac <- c()                              # average cost of different income groups as a list
  for (i in 2:6){
  ac <- cbind(ac, as.numeric(c(unlist(dataframe[column_names_vector[i]])))) #average cost for income groups
  }
  burden <- c()                              # list for the burden of different groups.
  for (i in 1:5){
    burden <- cbind(burden, (as.numeric(ac[,i]) - as.numeric(atc))/as.numeric(atc))
  }

  # Here we calculate a variance for the colleges:
  # I think I have another possible measure that accounts for inversions!
  # This is temporary as proof of concept!
  cumulitive <- rep(0, nrow(dataframe))
  for (i in 1:5){
    cumulitive <- cumulitive + abs(as.numeric(burden[,i]))
  }
  return(cumulitive)
}
X17.18.variance <- variance_of_colleges(scorecard, income_groups_17.18)

```

## Including Plots 17-18

You can also embed plots, for example:

```{r pressure, echo=FALSE}

resizing <- function(global_max, global_min, college_variance){
   #This function remaps the points between [min, max] to points between [0,1]
   (global_min-college_variance)/(global_min-global_max)
}

sum(is.na(X17.18.variance))
X17.18.variance.min <- summary(X17.18.variance)[[1]]
X17.18.variance.max <- summary(X17.18.variance )[[6]]

X17.18.accessibility.metric <- resizing(global_max = X17.18.variance.max , global_min = X17.18.variance.min, X17.18.variance)
summary(X17.18.accessibility.metric) 


```


```{r pressure, echo=FALSE}
summary(X09.10.accessibility.metric) 
summary(X10.11.accessibility.metric) 
summary(X11.12.accessibility.metric) 
summary(X12.13.accessibility.metric) 
summary(X13.14.accessibility.metric) 
summary(X14.15.accessibility.metric)
summary(X15.16.accessibility.metric)
summary(X16.17.accessibility.metric)
summary(X17.18.accessibility.metric)



```
